Constraining Black Hole Growth with High-z Quasar Observations

### 2022-08-16 ms.tex
version0807; k revise and recieve comments from DT,MO...

% \documentclass[linenumbers,preprint2,tighten,trackchanges]{aastex631}
%\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
\hypersetup{filecolor=cyan,urlcolor=magenta} %citecolor=green, linkcolor=red,
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}

@@

\correspondingauthor{}
\email{}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of the quasar luminosity and black hole mass function (MF) encodes key information
on the physics determining the radiative and accretion processes of supermassive black holes (SMBHs) in high-redshift quasars.
Although the shape of the luminosity function (LF) has been constrained by recent wide and deep surveys,
it still remains challenging to develop a theoretical model that explains the redshift evolution and BH growth self-consistently.
In this study, based on a semi-analytical model for the formation and growth of seed BHs
in quasar progenitor halos,
we construct the LF and MF of the early BH population that experiences multiple accretion bursts,
in each of which the Eddington ratio is assigned following a Schechter function.
Our best-fit model to reproduce the observed LF and MF at $z\simeq 6$
suggests that several episodes of modest super-Eddington accretion occur
and each of them lasts $\tau \simeq 20-30$ Myr.
The average duty cycle of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
which is nearly twice that of the entire population.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
The predicted redshift evolution of both LF and MF of earliest BHs suggests a rapid decay of their number and mass
toward higher redshifts of $z>6$, compared to galaxy stellar mass.
This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
% the , Roman Space Telescope (RST), and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive black holes (BHs) in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}.
%,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the quasar luminosity function based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained 
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022arXiv220607357S}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the quasar luminosity function \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

@@

\vspace{5mm}
\section{METHODOLOGY}\label{sec:method}

@@

\vspace{5mm}
\section{Results}\label{sec:result}

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
Left panel: BHMF at $z=$ 6 calculated in the $\fseed=0.01$ case, 
with different $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively, 
and other parameters are fixed to the best-fit values. 
The blue curve denotes the BHMF constrained by the \citetalias{2010AJ....140..546W} result. 
With lower(higher) $\tlife$ than the best-fit value, the BHMF is under(over)-produced in the high mass end.
Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
With $\tlife$ values different from the best-fit value, the consequent QLF show 
similar trends of deviation from observation as in the BHMF curves.
}
\label{fig:tau}
\vspace{4mm}
\end{figure*}

@@

%%%%%%%
%    Fig. 9
%%%%%%%
\begin{figure*}[h!]
\centering
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz7_KI.pdf}\hspace{5mm}
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz8_KI.pdf}\\\vspace{5mm}
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz9_KI.pdf}\hspace{5mm}
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz10_KI.pdf}
\caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
and the whole population (i.e., type-I and type-II AGNs), and the shaded region presents the $1\sigma$ spread.
The expected depths and volumes of future surveys with Wide RST and Wide Euclid are overlaid with the blue lines,
indicating the detectability of quasars at these redshifts.
Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
The galaxy luminosity function data at $z\sim$ 7 are taken from \citet[triangles]{2022ApJS..259...20H} \&
\citet[circles]{2021AJ....162...47B}, and the fitting functions are produced by \citet{2022ApJS..259...20H}. 
At $z\sim$ 8, the data points are from \citet[triangles]{2021AJ....162...47B},
\citet[circles]{2022arXiv220712356D}, \citet[pluses]{2013MNRAS.432.2696M}, \citet[diamond]{2020MNRAS.493.2059B}, and \citet[pentagons]{2019ApJ...883...99S},
as well as the fitting results by  \citet[double power law]{2020MNRAS.493.2059B} \& \citet[Schechter]{2013MNRAS.432.2696M}.
At  $z\sim$ 9, those data are from \citet[triangles]{Harikane_2022c}, \citet[circles]{2022arXiv220712356D}, \citet[pluses]{2020MNRAS.493.2059B}, \citet[diamonds]{2019ApJ...883...99S}, and \citet[pentagons]{2018ApJ...867..150M},
with the fitting functions from  \citet{Harikane_2022c}.
At $z\sim$ $10-13$, \citet[triangles]{Harikane_2022c},\citet[circles]{2022arXiv220712356D},\citet[pluses]{Harikane_2022b}, \citet[diamonds]{2022arXiv220709434N}, \citet[pentagons]{2018ApJ...867..150M}, and \citet[stars]{2016ApJ...819..129O},
and the fitting functions are produced by \citet{Harikane_2022c}.
}
\label{fig:LFs}
\end{figure*}

@@

\section{Summary}
In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
applying the initial mass function of seed BHs.
We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio
is assigned following a Schechter distribution function.
We conduct the MCMC fitting procedure used to optimize the BH growth parameters
so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced.
Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ yields the ERDF characterized with the two parameters of
$(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
The models suggests that several episodes of modest super-Eddington accretion occur and each accretion phase lasts $\simeq 20-30$ Myr.
For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
Therefore, multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
consistent with the observed distribution functions.
Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=-0.96$ for the quasar number.
The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
but tends to be slightly steeper at higher redshifts.
% \red{Add comparison to GLFs and expected detection numbers }\blue{
Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
which makes it more challenging to select such faint quasars.
The number of quasars dominates over that of galaxies in the bright end of the UV luminosity function.
We predict the critical magnitude at which galaxies and quasars equally contribute in number,
depending on extrapolation of the galaxy luminosity functions.
We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
with the best-fit parameters reproducing their statistical properties.
For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of accretion is as high as $\simeq 15~\%$.
Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
biased toward a population that undergoes active accretion episodes.
Multiple accretion-burst treatment nicely produces the mass assembly history of individual high$-z$ luminous quasars,
unlike the case where one single value of the Eddington ratio is assigned.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
Those results will be unveiled by future deep and wide surveys with the JWST, RST, and Euclid.

% \begin{acknowledgments}
% % We thank all the people that have made this paper what it is today.  
% % This includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
% % Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
% % Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
% % for the new "modern" style design. Considerable help was provided via bug
% % reports and hacks from numerous people including Patriciddo Cubillos, Alex
% % Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
% % Gagne.
% \end{acknowledgments}

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

@@

\clearpage

>>>>

% \documentclass[linenumbers,preprint2,tighten,trackchanges]{aastex631}
%\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
\hypersetup{filecolor=cyan,urlcolor=blue} %citecolor=green, linkcolor=red,
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}

@@

\correspondingauthor{Wenxiu Li; Kohei Inayoshi}
\email{wenxiuli@pku.edu.cn; inayoshi@pku.edu.cn}

@@

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of the quasar luminosity function (QLF) and black hole mass function (BHMF) encodes 
key information on the physics determining the radiative and accretion processes of supermassive 
black holes (SMBHs) in high-redshift quasars.
Although the shape of the QLF has been constrained by recent wide and deep surveys,
it still remains challenging to develop a theoretical model that explains its redshift evolution with BH growth self-consistently.
In this study, based on a semi-analytical model for the formation and growth of seed BHs
in quasar progenitor halos,
we construct the QLF and BHMF of the early BH population that experiences multiple accretion bursts,
in each of which constant Eddington ratio is assigned following a Schechter distribution function.
Our best-fit model to reproduce the observed QLF and BHMF at $z\simeq 6$
suggests that several episodes of modest super-Eddington accretion occur
and each of them lasts $\tau \simeq 20-30$ Myr.
The average duty cycle of BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$ is as high as $\simeq 15~\%$,
which is nearly twice that of the entire population.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
The predicted redshift evolution of both QLF and BHMF of earliest BHs suggests a rapid decay of their number and mass
toward higher redshifts of $z>6$, compared to galaxy stellar mass.
This will be unveiled by future deep and wide surveys with the James Webb Space Telescope, Roman Space Telescope, and Euclid.
% the , Roman Space Telescope (RST), and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive BHs in active galactic nuclei (AGN) is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}.
%,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the QLF based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained 
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T,2022arXiv220607357S}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D}
along with the QLF \citep[e.g.,][]{2015ApJ...798...28K,2018ApJ...869..150M}.
%and the virial BH mass estimates
%from the \ion{Mg}{2} 2798 $\rm{\AA}$ line width 
%where 
Deep spectroscopic observations of high-$z$ quasars enable us to measure the virial BH mass 
with the \ion{Mg}{2} single-epoch method and bring insights of the mass distribution
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.

@@

\vspace{2mm}
\section{METHODOLOGY}\label{sec:method}

@@

\vspace{2mm}
\section{Results}\label{sec:result}

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{tau.png}
\caption{
The BH mass function (left) and quasar luminosity function (right) at $z=$ 6 in the case of $\fseed=0.01$, 
with different values of $\tlife=$ 10, 18 (the best-fit value), and 50 Myr, respectively.
Note that the other parameters are fixed to the best-fit values. 
The $z=6$ BHMF (\citetalias{2010AJ....140..546W}) and QLF (\citetalias{2018ApJ...869..150M}) 
are overlaid with the blue curve and data points.
With shorter (longer) timescales of each accretion episode $\tlife$, the number of BHs at the high mass end and bright end is under(over)-produced.
%Right panel: QLF at $z=$ 6 calculated with the same parameters as in the left panel.
%The overlaid blue dots are from the \citetalias{2018ApJ...869..150M} $z\sim$ 6 quasar observation. 
%With $\tlife$ values different from the best-fit value, the consequent QLF show 
%similar trends of deviation from observation as in the BHMF curves.
Multiple accretion bursts in each duration of $\tau \simeq 20$ Myr best produce the observations,
which is nearly half of the $e$-folding time of the exponential BH mass growth.
}
\label{fig:tau}
\vspace{4mm}
\end{figure*}

@@

%%%%%%%
%    Fig. 9
%%%%%%%
\begin{figure*}[h!]
\centering
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz7_KI.pdf}\hspace{5mm}
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz8_KI.pdf}\\\vspace{5mm}
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz9_KI.pdf}\hspace{5mm}
\includegraphics[width=85mm]{M0r8_f2linLF_spreadz10_KI.pdf}
\caption{Predicted quasar luminosity functions and depths and volumes of upcoming surveys.
The black solid and dashed curves present the QLF for the unobscured population (e.g., type-I AGNs) 
and the whole population (i.e., type-I and type-II AGNs), and the shaded region presents the $1\sigma$ spread.
The expected depths and volumes of future surveys with Wide RST and Wide Euclid are overlaid with the blue lines,
indicating the detectability of quasars at these redshifts.
Galaxy UV luminosity functions are plotted with the data points (grey) and fitting functions with a Schechter (dotted curve) and double power-law (dash-dotted curve) shape.
The galaxy luminosity function data at $z\sim$ 7 are taken from \citet{2022ApJS..259...20H} and \citet{2021AJ....162...47B}. 
At $z\sim$ 8, the data points are from \citet{2021AJ....162...47B},
\citet{2022arXiv220712356D}, \citet{2013MNRAS.432.2696M}, \citet{2020MNRAS.493.2059B}, and \citet{2019ApJ...883...99S}.
At  $z\sim$ 9, those data are from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{2020MNRAS.493.2059B}, \citet{2019ApJ...883...99S}, 
and \citet{2018ApJ...867..150M}.
At $z\sim$ $10-13$, we take data from \citet{Harikane_2022c}, \citet{2022arXiv220712356D}, \citet{Harikane_2022b}, \citet{2022arXiv220709434N}, \citet{2018ApJ...867..150M}, 
and \citet{2016ApJ...819..129O}.
The fitting forms of the luminosity functions are given by \citet{2022ApJS..259...20H} at $z\simeq 7$, 
\citet{2020MNRAS.493.2059B} and \citet{2013MNRAS.432.2696M} at $z\simeq 8$, and \citet{Harikane_2022c} at $9\lesssim z\lesssim 13$.
}
\label{fig:LFs}
\end{figure*}

@@

\section{Summary}
In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
applying the initial mass function of seed BHs.
We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio
is assigned following a Schechter distribution function.
We conduct the MCMC fitting procedure used to optimize the BH growth parameters
so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced.
Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ yields the ERDF characterized with the two parameters of
$(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
The models suggests that several episodes of modest super-Eddington accretion occur and each accretion phase lasts $\simeq 20-30$ Myr.
For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
Therefore, multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
consistent with the observed distribution functions.
Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=-0.96$ for the quasar number.
The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
but tends to be slightly steeper at higher redshifts.
% \red{Add comparison to GLFs and expected detection numbers }\blue{
Compared to the galaxy luminosity functions at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict are burried in the faint end at $\Muv \gtrsim -23$ mag,
which makes it more challenging to select such faint quasars.
The number of quasars dominates over that of galaxies in the bright end of the UV luminosity function.
We predict the critical magnitude at which galaxies and quasars equally contribute in number,
depending on extrapolation of the galaxy luminosity functions.
We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
with the best-fit parameters reproducing their statistical properties.
For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of accretion is as high as $\simeq 15~\%$.
Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
biased toward a population that undergoes active accretion episodes.
Multiple accretion-burst treatment nicely produces the mass assembly history of individual high-$z$ luminous quasars,
unlike the case where one single value of the Eddington ratio is assigned.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
Those results will be unveiled by future deep and wide surveys with the JWST, RST, and Euclid.

\acknowledgments
We greatly thank Jin Wu, AAA, BBB, and CCC for constructive discussions. 
We acknowledge support from the National Natural Science Foundation of China 
(12073003, 12003003, 11721303, 11991052, 11950410493, and 1215041030), 
and the China Manned Space Project Nos. CMS-CSST-2021-A04 and CMS-CSST-2021-A06. 
The numerical simulations were performed with the Cray XC50 at the Center for Computational Astrophysics (CfCA) 
of the National Astronomical Observatory of Japan and with the High-performance Computing Platform of Peking University.
%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

@@

% \clearpage
